### 2016-09-27 review/response_to_reviewer.txt

   This is indeed an interesting point. In the present study, we give
   a first order description of the effect of synchrony on stationary
   firing rate (in the /weakly synchronous/ regime, close to an
   idealized /asynchronous/ regime): presynaptic synchrony between
   presynaptic events increases the variance of the fluctuations that
   in turn increases the firing rate. But there should be effect
   beyond this first order description, when we go further and further
   from the idealized asynchronous state, i.e. when the firing rate
   can not be obtained from the stationary fluctuations
   properties. Interactions between synchrony and dendritic
   non-linearities also appear important to neocortical cell
   processing (see Part A of this response). Following the reviewer's
   opinion, we would also prefer to leave this issue aside as those
   are quite complicated questions and perform detailed investigations
   in future work.

@@

** Major concern

\it My only major concern with the paper is on the emphasis of a
theoretical framework without citing other relevant work in the
area. Essentially I am surprised not to see the mention of the
technique(s) for constructing the Green's function of an arbitrary
branched passive dendritic tree. The paper focuses on Rall equivalent
cylinders for simplicity, yet the methodology presented would seem
easily extended using the work of Abbott [[cite:Abbott1991,Cao1993]]. The
extension of the above to include a distinguished soma model can be
found in [[citetext:Coombes2007]] and Paul Bressloff has done a lot of
work on dendrites that appears relevant, some of which is summarised
in [[citetext:Bressloff1997]]. The following may also be of interest
(though not necessarily for this work) - where simple active soma
models are coupled to passive dendrites
[[cite:Bressloff1995,Svensson2009,Schwemmer2012]]. \rm

We are grateful to the reviewer for those bibliographical
suggestions. This allowed us to detail the possible extension of our
framework to more complex dendritic structures. The updated discussion
now reads (line 335): \bf To investigate those effects within the
framework proposed in our study, one could benefit from the large body
of theoretical work on the derivation of Green’s function for
arbitrary branched passive dendritic trees
[[cite:Abbott1991,Cao1993,Bressloff1997,Coombes2007]]. \rm

Nonetheless, for clarity for the reader (not to be pointed toward more
complex methods than just Rall's method), we keep only the reference
to Rall's work in the Methods and Results section. Then the author can
be more focused on the originality of our approach: the use of
shotnoise theory results in a dendritic integration context.

In addition, we have given some perspective about the approach used
here to obtain the firing rate response in presence of a dendritic
structure. In the discussion, one can now find the sentence (line
361):

\bf This phenomenological two-steps procedure thus offers a flexible
complementary approach to the analytical approaches tackling the
problem of the spiking behavior in presence of an extended dendritic
structure [[cite:Svensson2009,Schwemmer2012,Saparov2015]]. \rm

@@

** Minor points

1) \it Spurious "s" in the sec "A simplified morphological model" - sWe arbitrarily ... \rm

Thanks. corrected.

2) \it Where is excitability < V_thre^eff >_D defined? \rm

Thanks. This was indeed only briefly mentionned in a main text as a
reference to our previous study, now in the Methods section, we added:

\bf Importantly, our study introduced four quantities to describe the
mean properties of a single neuron response in the fluctuation-driven
regime: (i) a measure of the excitability given by the mean
phenomenological threshold \( \langle V_{thre}^eff \rangle_\mathcal{D}
\) of our firing rate function, (ii) a sensitivity to the mean of the
fluctuations \( \langle \frac{\partial \nu}{\partial \mu_V}
\rangle_\mathcal{D} \), i.e. quantifying how much a mean
depolarization is translated into a change in firing rate, (iii) a
sensitivity to the amplitude of the fluctuations \( \langle
\frac{\partial \nu}{\partial \sigma_V} \rangle_\mathcal{D} \),
quantifying how much an increase of the standard deviation of the
fluctuations is translated into a change in firing rate, and (iv) a
sensitivity to the speed of the fluctuations \( \langle \frac{\partial
\nu}{\partial \tau_V^N} \rangle_\mathcal{D} \), quantifying how much a
change in the autocorrelation time of the fluctuations is translated
into a change in firing rate. \rm

@@

The topic is of importance and the theoretical part is novel, very
appealing in itself and rigorous, but inadequate to support the key
claim of the paper (see paper title).

This is because ... \rm

** CONS

 - *A*: \it (part ii) For L5 PCs it is highly questionable if dendritic
   integration can be understood without (or separated from) active
   dendritic properties given the known experimental facts and huge
   literature, e.g. about the compartmentalization of dendritic
   function, dendritic spikes, and changed response properties due to
   ion channel blockers.

   In my opinion, the model for the L5 PCs based on a passive tree
   will almost surely fail to describe the real dendritic integration
   properties of the cells in the fluctuation driven regime. In any
   case, see the first point in additional work below. \rm

   We adressed in details the question of dendritic nonlinearities in
   Part A. The question of the compartementalization of dendritic
   function is indeed something not adressed in our study, we would
   prefer to leave this aspect for future investigations.

- *B*: \it (part iii) Even the description of the passive dendritic
  integration properties of the cell seems to be questionable (maybe
  because of the constraints to symmetrical trees). That this doesn't
  work out properly seems to be reflected in the morphologies obtained
  in the paper: Is the required variation of the tree length from
  about 400 um to 900 um (current Fig 3C and Fig. S1) for PCs
  plausible? Please provide references. L5 PCs with their long apical
  dendrites etc. are the worst case scenario for the symmetry
  constraints for the tree. \rm

  We totally agree with the reviewer on this point. We removed the
  point stating that our simplified morphology could somehow resemble
  those of layer V pyramidal cells. More precisely, we removed the
  following statement: \bf Also the obtained morphology seems
  realistic (B=5 generation of branches, a total tree length of =550m
  and a root branch diameter of the tree =2.25m) given what can be
  observed after histological work [[cite:Zerlaut2016]] \rm. The emphasis
  should remain on the electrical properties.

  Importantly, the results of our study do not rely on having a
  precise description of the morphology, we only use this to
  discriminate between a proximal and a distal area, and Rall's
  symmetric branching model is sufficient to reproduce this feature.
  So in the discussion, we aknowledge the important limitations of our
  morphological model and stress the above point (what is the
  important ingredient in our study) with:

 \bf [...] even if our description captures the various electrotonic
  distances associated to various synaptic locations (the crucial
  ingredient here to discriminate between proximal and distal inputs),
  the morphological model appears as a _very poor description of layer
  V pyramidal cell_. Deviations from the symmetric branching
  hypothesis and Rall's branching rule will have a significant impact
  on dendritic integration in the fluctuation-driven regime. To
  investigate those effects [...] \rm

@@

** PROS

\it The theoretical work is still significant for other cell types that
work in a more linear regime, e.g. L2/3 PCs, and have morphologies
that match the theoretical constraints.. \rm

@@

** Additional work required:

- \it The authors should provide evidence that active dendritic
  integration doesn't change the key claim, or, apply the model to a
  more appropriate cell type. \rm

  see Part A of this response

- \it Because the morphology of the tree of the model is very
  constraint and only a very rough estimate its necessary to assess
  the influence of this approximation on dendritic integration: A
  systematic analysis of the impact of the morphology of the tree (7
  variables) on the response properties of interest at the soma is
  missing (This allows also a generalization of the results to other
  cell types. Now only Fig S2 gives a hint about variability). \rm

  *TO BE DONE*

- \it There's no reference to any other model than [[citetext:Kuhn2004]],
  on which the approach is based. Relate the model to recent work on
  the effects of passive dendritic tree properties of neuron on firing
  dynamics (e.g.  [[citetext:Saparov2015]] or other model reduction
  techniques (a huge field, e.g. [[citetext:Hedrick2013]]). \rm

  The updated discussion now reads (line 335): \bf To investigate
  those effects within the framework proposed in our study, one could
  benefit from the large body of theoretical work on the derivation of
  Green’s function for arbitrary branched passive dendritic trees
  [[cite:Abbott1991,Cao1993,Bressloff1997,Coombes2007]]. \rm In addition,
  we have given some perspective about the approach used here to
  obtain the firing rate response in presence of a dendritic
  structure. In the discussion, one can now find the sentence (line
  361): \bf This phenomenological two-steps procedure thus offers a
  flexible complementary approach to the analytical approaches
  tackling the problem of the spiking behavior in presence of an
  extended dendritic structure
  [[cite:Svensson2009,Schwemmer2012,Saparov2015]]. \rm

\it The paper is well organized, easy to read, simple to follow and
clearly written.

However, there are too many typos and word repetitions to list them
all ("sWe" p.3, "show deviations from the deviations" p.4, " vary the
size of the size" p.4, "does not goes", p.6, "the firing increase
show", p.7 ...) and the Figure numbers were incorrect (Fig.22b, p.4)
or mixed up (Fig. 2 and 3). \rm

We apologize for the problems in the manuscript preparation (the
figures mixed up) and we thank the reviewer for pointing out the
typos... From now on, even if the question refer to the (wrong)
previous notation ex-Figure 3 will be renamed to Figure 2 as in the
re-submission.

** Minor:

- \it Fig. 3: The color code seems to be inconsistent: Panel A shows cells
  with Rm above 600 MOhm, but the bottom panel in Fig 3C shows that
  such cells are not present. \rm

  This is because those data come from two separate datasets, we
  highlighted this with the mention of "firing rate dataset" at the
  bottom of panel 2C. We have a special dataset to investigate the
  input impedance properties (on the exact same experimental model)
  where 2 cells were more resistive than those present in the other
  dataset. We use this dataset to derive a "sizing rule" from the
  input resistance and then be able to use the "firing rate dataset"
  where we only have the input resistance (and not the detailed input
  impedance spectrum). Note that, as expected from the same
  exerimental system, the datasets were statistically pretty similar:
  355.9 \(\pm\) 184.1 M\(\Omega\) for the "firing rate dataset", see
  [[citetext:Zerlaut2016]] and 387.3 \(\pm\) 197.2 M\(\Omega\) for the
  "input impedance dataset", see Methods.

  We have updated figure 2C with the mention of "n=30cells" for the
  "firing rate dataset", then it highlights the difference with the
  dataset of input impedance labeled "n=13cells" and makes it more
  clear to the reader.

- \it Fig 3C: The lines in the three top panels could be drawn with the
  color code (color changes within a line) as used in panel A and B. \rm

  Very good idea, thanks ! See new Figure 2.

- \it Fig 3AB: Please comment on the inconsistency between data and model
  for > 100 Hz. There seems to be a flip in vertical order. \rm

  *TO BE DONE*

\it Section: "An analytical approximation ...":

- The claim "the analytical estimate could therefore be seen as an
  accurate estimate, modulo a shift in the synchrony (~0.2 increase in
  synchrony corrects for the ~1 mV shift in sigma)" should
  verified: 1) Results for synchrony = 0.2 should be shown in the
  right most column of panels in Fig 2B, and 2) results for synchrony
  = 0.2 should be shown for the other columns of panels in Fig 2B,
  where the other parameters are varied. \rm

  *TO BE DONE*

@@

Section: "Biophysical origin ..."

- \it The characteristics of the firing response function are not properly
  introduced. Please add this. \rm

  This is indeed a very important point, thanks, we updated the
  methods section with:

  \bf Importantly, our study introduced four quantities to describe
  the mean properties of a single neuron response in the
  fluctuation-driven regime: (i) a measure of the excitability given
  by the mean phenomenological threshold \( \langle V_{thre}^eff
  \rangle_\mathcal{D} \) of our firing rate function, (ii) a
  sensitivity to the mean of the fluctuations \( \langle
  \frac{\partial \nu}{\partial \mu_V} \rangle_\mathcal{D} \),
  i.e. quantifying how much a mean depolarization is translated into a
  change in firing rate, (iii) a sensitivity to the amplitude of the
  fluctuations \( \langle \frac{\partial \nu}{\partial \sigma_V}
  \rangle_\mathcal{D} \), quantifying how much an increase of the
  standard deviation of the fluctuations is translated into a change
  in firing rate, and (iv) a sensitivity to the speed of the
  fluctuations \( \langle \frac{\partial \nu}{\partial \tau_V^N}
  \rangle_\mathcal{D} \), quantifying how much a change in the
  autocorrelation time of the fluctuations is translated into a change
  in firing rate. \rm

- \it It can be hardly claimed that Fig. 6A is approximately a log normal
  distribution. \rm

  We agree. What we actually mean is that the data appears to be
  distributed logarithmically, we do not wish to put a special
  emphasis on the log-normal trend. The statement "approximatelly
  log-normal" was a concise way to express this trend. If this is a
  problem, we could change it to "the data appears to be distributed
  logarithmically and not linearly" but we are not sure that this
  formulation would render better the idea.

\it Methods section: \rm

- \it Not all variables are properly defined, e.g. Qe, Qi, lp. \rm

  Indeed, thanks. We updated the Methods section (mostly the "Model
  equations" section).

- \it "it constitutes an extension of the approach proposed in Kuhn et
  al.": Please, state what extension. \rm

  Done, it now reads: \bf it extends the approach proposed in Kuhn et
  al. to the extended dendritic structure following Rall’s branching
  rule \rm

- \it "Fitting passive properties": Are the solutions unique or are there
  many different trees with similar fit performance that result in
  different couplings to presynaptic activity? \rm

  *TO BE DONE*

@@

* References
\small

#+BEGIN_LATEX
\begin{filecontents}{biblio.bib}

@article{Hausser2005,
author = {London, Michael and H{\"{a}}usser, Michael},
doi = {10.1146/annurev.neuro.28.061604.135703},
issn = {0147-006X (Print)$\backslash$r0147-006X (Linking)},
journal = {Annual review of neuroscience},
pages = {503--532},
title = {{Dendritic computation.}},
type = {Journal Article},
volume = {28},
year = {2005}
}

### 2016-09-27 review/response_to_reviewer.txt

4) \it No dendritic nonlinearities. One main characteristics of L5
   pyramidal neurons is the calcium spike in the apical tree, and more
   generally the various types of dendritic spikes. Non of them is
   considered in the model, and one conjectures that the various
   response properties in the experimental data arise from these
   various dendritic nonlinearities. Describing the firing properties
   of pyramidal neurons as a function of proximal and distal activity
   should take account of these dendritic nonlinearities. Otherwise,
   in fact, the statements cannot be compelling. \rm

   We adressed this concern in details in Part A.

5) \it Data extraction. It is not clear how the 4 cells have been selected
   out of the 27 cells. The 4 cells represent 4 cell types. How are
   these cell types specified? The paper does not give an answer on
   that. \rm

   The 4 cells represent 4 different cells out of the n=27 cells
   recorded in our previous study [[cite:Zerlaut2016]]. The criteria to
   choose those 4 cells was that they should somehow represent
   different behaviors while still being representative. See in Figure
   6B in [[citetext:Zerlaut2016]] how those 4 cells cover relatively well
   the domain of measured characteristics for the firing response,
   this is also the case in the present study, where they cover
   relatively well the domain of the predicted coupling to the various
   types of activities, see Figure 6 in main text. We updated the
   manuscript to highlight this point (line 250): \bf We show on
   Figure 5 the response of four cells (representative of different
   firing response behaviors, see Figure 5 and 6B in
   [[citetext:Zerlaut2016]]) to the different types of presynaptic
   activity described in the previous section. The input-output
   relationships show qualitative and quantitative differences, [...]
   \rm

@@

** Minor:

- \it Fig. 3: The color code seems to be inconsistent: Panel A shows cells
  with Rm above 600 MOhm, but the bottom panel in Fig 3C shows that
  such cells are not present. \rm

  This is because those data come from two separate datasets, we
  highlighted this with the mention of "firing rate dataset" at the
  bottom of panel 2C. We have a special dataset to investigate the
  input impedance properties (on the exact same experimental model)
  where 2 cells were more resistive than those present in the other
  dataset. We use this dataset to derive a "sizing rule" from the
  input resistance and then be able to use the "firing rate dataset"
  where we only have the input resistance (and not the detailed input
  impedance spectrum). Note that, as expected from the same
  exerimental system, the datasets were statistically pretty similar:
  355.9 \(\pm\) 184.1 M\(\Omega\) for the "firing rate dataset", see
  [[citetext:Zerlaut2016]] and 387.3 \(\pm\) 197.2 M\(\Omega\) for the
  "input impedance dataset", see Methods.

  We have updated figure 2C with the mention of "n=27cells" for the
  "firing rate dataset", then it highlights the difference with the
  dataset of input impedance labeled "n=13cells" and makes it more
  clear to the reader.

@@

  *TO BE DONE*

\it Section: "An analytical approximation ...":

- The claim "the analytical estimate could therefore be seen as an
  accurate estimate, modulo a shift in the synchrony (~0.2 increase in
  synchrony corrects for the ~1 mV shift in sigma)" should
  verified: 1) Results for synchrony = 0.2 should be shown in the
  right most column of panels in Fig 2B, and 2) results for synchrony
  = 0.2 should be shown for the other columns of panels in Fig 2B,
  where the other parameters are varied. \rm

  We have verified this statement and we now present the results on
  Figure 3. The shift in synchrony that minimized the difference
  between analytical simulations and numerical simulations was found
  to be +0.18, i.e. close to the 0.2 previously mentionned in the main
  text (minimum found thanks to a Newton method). Those additional
  curves are now presented in the middle plots of Figure 3B with the
  label "estimate, s+=0.18". We also increased the resolution of the
  scanned points so that we can also have a point close to the s=0.18
  in the right most column of Figure 3B.  The text now reads (line
  182): \bf (see Figure 3B, an increase of 0.18 in the synchrony
  corrects for the ~1mV shift in \(\sigma_V\)) \rm and the legend: \bf
  In the \(\sigma_V\) plots (middle panels, dashed gray lines), we
  added the prediction of the analytical estimate after a +0.18
  correction (found with a Newton method). \rm

\it Section: "Biophysical origin ..." \rm

@@

  This is indeed a very important point, thanks, we updated the
  methods section with:

  \bf Importantly, our study introduced four quantities to describe
  the mean properties of a single neuron response in the
  fluctuation-driven regime: (i) a measure of the excitability given
  by the mean phenomenological threshold \( \langle V_{thre}^eff
  \rangle_\mathcal{D} \) of our firing rate function, (ii) a
  sensitivity to the mean of the fluctuations \( \langle
  \frac{\partial \nu}{\partial \mu_V} \rangle_\mathcal{D} \),
  i.e. quantifying how much a mean depolarization is translated into a
  change in firing rate, (iii) a sensitivity to the amplitude of the
  fluctuations \( \langle \frac{\partial \nu}{\partial \sigma_V}
  \rangle_\mathcal{D} \), quantifying how much an increase of the
  standard deviation of the fluctuations is translated into a change
  in firing rate, and (iv) a sensitivity to the speed of the
  fluctuations \( \langle \frac{\partial \nu}{\partial \tau_V^N}
  \rangle_\mathcal{D} \), quantifying how much a change in the
  autocorrelation time of the fluctuations is translated into a change
  in firing rate. \rm

- \it It can be hardly claimed that Fig. 6A is approximately a log normal
  distribution. \rm

  We agree. What we actually mean is that the data appears to be
  distributed logarithmically, we do not wish to put a special
  emphasis on the log-normal trend. The statement "approximatelly
  log-normal" was a concise way to express this trend. If this is a
  problem, we could change it to "the data appears to be distributed
  logarithmically and not linearly" but we are not sure that this
  formulation is a "standard formulation".

@@

\it Methods section: \rm

- \it Not all variables are properly defined, e.g. Qe, Qi, lp. \rm

  Indeed, thanks. We updated the Methods section. Also the densities
  of synapses were not properly introduced.

### 2016-09-28 review/response_to_reviewer.txt

   This point is precisely the focus of our previous communication
   [[cite:Zerlaut2016]]. Unfortunately there is, to the best of our
   knowledge, no closed-form solution that could give the firing rate
   response as a response to fluctuating input in a model including
   sodium inactivation and a sodium activation curve (hence the
   phenomenological approach formulated in our previous
   communication). Nonetheless to give some intuition to the reader,
   we have added the following statement (line 316): \bf In our
   previous communication, theoretical modeling suggested that a high
   sensitivity to the speed of the fluctuations was enable by a high
   level of sodium inactivation (as only fast fluctuations allow to
   deinactivate sodium channels) and a high density of sodium channels
   (as it produces a sharp spike initiation that enables to extract
   fast fluctuating input). \rm For further details, we believe the
   reader should refer to our previous publication.

4) \it No dendritic nonlinearities. One main characteristics of L5
   pyramidal neurons is the calcium spike in the apical tree, and more
   generally the various types of dendritic spikes. Non of them is
   considered in the model, and one conjectures that the various
   response properties in the experimental data arise from these
   various dendritic nonlinearities. Describing the firing properties
   of pyramidal neurons as a function of proximal and distal activity
   should take account of these dendritic nonlinearities. Otherwise,
   in fact, the statements cannot be compelling. \rm

   We adressed this concern in details in Part A.

5) \it Data extraction. It is not clear how the 4 cells have been selected
   out of the 30 cells. The 4 cells represent 4 cell types. How are
   these cell types specified? The paper does not give an answer on
   that. \rm

   The 4 cells represent 4 different cells out of the n=30 cells
   recorded in our previous study [[cite:Zerlaut2016]]. The criteria to
   choose those 4 cells was that they should somehow represent
   different behaviors while still being representative. See in Figure
   6B in [[citetext:Zerlaut2016]] how those 4 cells cover relatively well
   the domain of measured characteristics for the firing response,
   this is also the case in the present study, where they cover
   relatively well the domain of the predicted coupling to the various
   types of activities, see Figure 6 in main text. We updated the
   manuscript to highlight this point (line 250): \bf We show on
   Figure 5 the response of four cells (representative of different
   firing response behaviors, see Figure 5 and 6B in
   [[citetext:Zerlaut2016]]) to the different types of presynaptic
   activity described in the previous section. The input-output
   relationships show qualitative and quantitative differences, [...]
   \rm

@@

- \it The authors should provide evidence that active dendritic
  integration doesn't change the key claim, or, apply the model to a
  more appropriate cell type. \rm

  see Part A of this response

- \it Because the morphology of the tree of the model is very
  constraint and only a very rough estimate its necessary to assess
  the influence of this approximation on dendritic integration: A
  systematic analysis of the impact of the morphology of the tree (7
  variables) on the response properties of interest at the soma is
  missing (This allows also a generalization of the results to other
  cell types. Now only Fig S2 gives a hint about variability). \rm

#+NAME: fig:var-morpho
#+CAPTION: *Varying morphology.*
[[./figs/var_morph.png]]

@@

** Minor:

- \it Fig. 3: The color code seems to be inconsistent: Panel A shows cells
  with Rm above 600 MOhm, but the bottom panel in Fig 3C shows that
  such cells are not present. \rm

  This is because those data come from two separate datasets, we
  highlighted this with the mention of "firing rate dataset" at the
  bottom of panel 2C. We have a special dataset to investigate the
  input impedance properties (on the exact same experimental model)
  where 2 cells were more resistive than those present in the other
  dataset. We use this dataset to derive a "sizing rule" from the
  input resistance and then be able to use the "firing rate dataset"
  where we only have the input resistance (and not the detailed input
  impedance spectrum). Note that, as expected from the same
  exerimental system, the datasets were statistically pretty similar:
  355.9 \(\pm\) 184.1 M\(\Omega\) for the "firing rate dataset", see
  [[citetext:Zerlaut2016]] and 387.3 \(\pm\) 197.2 M\(\Omega\) for the
  "input impedance dataset", see Methods.

  We have updated figure 2C with the mention of "n=30cells" for the
  "firing rate dataset", then it highlights the difference with the
  dataset of input impedance labeled "n=13cells" and makes it more
  clear to the reader.

@@

- \it "it constitutes an extension of the approach proposed in Kuhn et
  al.": Please, state what extension. \rm

  Done, it now reads: \bf it extends the approach proposed in Kuhn et
  al. to dendritic structures following Rall’s branching rule \rm

- \it "Fitting passive properties": Are the solutions unique or are there
  many different trees with similar fit performance that result in
  different couplings to presynaptic activity? \rm

#+NAME: fig:fitting
#+CAPTION: *Fitting.*
[[./figs/fitting.png]]

### 2016-09-29 review/response_to_reviewer.txt

   \bf The abscissa “increasing synaptic quantity” corresponds to the
   comodulations of the model variables shown in Figure 4A (same color
   code). As an example, the response to a “proximal activity
   increase” (blue curve) corresponds to a linear increase of
   \(\nu_e^{prox}\) and \(\nu_i^{prox}\) while keeping
   \(\nu_e^{dist}\), \(\nu_i^{dist}\) and \(s\) to their baseline
   level. See Figure 4A for the comodulations of the other types of
   increasing activity. \rm

2) \it Main statement unclear. Unfortunately, it does not become clear
   what one has to understand of the “Diverse Couplings to the
   Presynaptic Activity” as expressed in the title. In the abstract it
   is stated: “We indeed found such a heterogeneous response, but
   trivially, the only significant contribution to the various firing
   response was the different levels of cellular excitability.” We
   guess that the “trivially” refers to the fact that only the
   cellular excitability has been modulated in the model. But then we
   don’t understand “A notable exception appeared for proximal
   activity: increasing proximal activity could either promote firing
   response in some cells or suppress it in some other cells whatever
   their individual excitability.” We conclude that there is still
   more than the individual excitability that determines the firing
   behavior, but this seems to contradict the previous statement. \rm

   We agree and have reworded the abstract and discussion to better
   highlight our main finding and better explicit what we mean by
   "diverse coupling". We also removed the formulation "only [...]
   except [...]" that might be misleading. We hope it is now more
   clear.

@@

- \it The authors should provide evidence that active dendritic
  integration doesn't change the key claim, or, apply the model to a
  more appropriate cell type. \rm

  see Part A of this response

- \it Because the morphology of the tree of the model is very
  constraint and only a very rough estimate its necessary to assess
  the influence of this approximation on dendritic integration: A
  systematic analysis of the impact of the morphology of the tree (7
  variables) on the response properties of interest at the soma is
  missing (This allows also a generalization of the results to other
  cell types. Now only Fig S2 gives a hint about variability). \rm

  We performed this systematic analysis, the results are shown in
  Figure [[fig:var-morpho]]. We adapted the supplemetary figure S2 in the
  manuscript, to include those results.

#+NAME: fig:var-morpho
#+CAPTION: *Dependency of the fluctuations properties as a function of the morphology parameters* (all parameters are varied of -70% and +70% around those of the mean model, one parameter is varied while all others are fixed to those of the mean model, see Table 1). We fixed the presynaptic stimulation to a level of \(\nu_e^p=\nu_e^d\)=0.2Hz, \(\nu_i^p=\nu_i^d\)=1.2Hz and s=0.05. (the baseline level). Globally, the mean polarization  is poorly affected by the morphology, given the balanced nature of the input and the homogenous spread of synapses on the membrane. On the other hand, the morphology parameters strongly affect the properties of the amplitude and speed of the fluctuations. (i) Dependency on the branching number. Because the branching number has an impact on the area, the number of synapses increases with the number of branches, then the amplitude of the fluctuations strongly decreases with the number of branches because of the law of large numbers. (ii) Dependency on the tree length. The same argument as in (i) holds. The length of the tree increases the number of synapses so that it reduces the amplitude of synapses. (iii) Dependency on the tree diameter. The same argument as in (i) holds again. The diameter of the tree increases the number of synapses so that it reduces the amplitude of synapses. (iv) Dependency on the size of the soma. Here, this increases only the number of inhibitory synapses at the soma. Within this range this has very weak effects on the fluctuations. (v) Dependency on the leak conductance. The leak conductance sets the amplitude and low pass filtering of individual post-synaptic events (because \(\tau_m \sim C_m / G_L\), though see correction introduced by the ongoing activity in the main text). An increasing leak conductance will “shunt” post-synaptic events. This lowers the amplitude of the fluctuations and lowers the autocorrelation time of the fluctuations. (vi) Dependency on the specific capacitance. Again because \(\tau_m \sim C_m / G_L\), an increasing capacitance renders the fluctuations much slower (increasing \(\tau_V\) ). Also because PSP events are much slower they lead to reduced amplitude of the fluctuations . (vii) Dependency on the intracellular resistivity. This has a moderate effect within this range.*
[[./figs/var_morph.png]]

@@

- \it Fig 3C: The lines in the three top panels could be drawn with the
  color code (color changes within a line) as used in panel A and B. \rm

  Very good idea, thanks ! See new Figure 2.

- \it Fig 3AB: Please comment on the inconsistency between data and model
  for > 100 Hz. There seems to be a flip in vertical order. \rm

  We now comment on the flip in vertical order (line 138): \bf In
  particular, it strongly underestimates the variations of phase
  shifts at medium and high frequencies (f>20Hz) and the relationship
  between size and modulus at high frequencies (f>100Hz) is poorly
  captured. Those discrepancies are likely to be due to the details of
  dendritic arborescence that are not captured by the strong
  constraints of our dendritic model (symmetric branching, diameter
  rules, number of branches, etc...). \rm

@@

  We agree. What we actually mean is that the data appears to be
  distributed logarithmically, we do not wish to put a special
  emphasis on the log-normal trend. The statement "approximatelly
  log-normal" was a concise way to express this trend. If this is a
  problem, we could change it to "the data appears to be distributed
  logarithmically and not linearly" but we are not sure that this
  formulation is a "standard formulation".

\it Methods section: \rm

- \it Not all variables are properly defined, e.g. Qe, Qi, lp. \rm

  Indeed, thanks. We updated the Methods section. Also the densities
  of synapses and some cable theory parameters have been properly
  introduced.

@@

- \it "it constitutes an extension of the approach proposed in Kuhn et
  al.": Please, state what extension. \rm

  Done, it now reads: \bf it extends the approach proposed in Kuhn et
  al. to dendritic structures following Rall’s branching rule \rm

- \it "Fitting passive properties": Are the solutions unique or are there
  many different trees with similar fit performance that result in
  different couplings to presynaptic activity? \rm

  To get different couplings, the new tree would need to break the
  relationship between presynaptic quantities and fluctuations
  properties (the relationship from fluctuations to spikes is
  independent). We thus studied the properties of the fluctuations for
  the trees that had similar goodness to fit with respect to the "mean
  model" of the main text. We present those results in Figure
  [[fig:fitting]]. Despite some differences, the fluctuations had similar
  trends than those discussed within the main text, in particular they
  all showed the crucial ingredient of this study: the very strong
  increase in fluctuations speed as a function of proximal activity.

#+ATTR_LATEX: :width .8\linewidth
#+NAME: fig:fitting
#+CAPTION: *Fluctuations properties for the morphologies with similar goodness to fit.* *(A)* Fluctuation propertis for two randomly choosen cells within the high goodness to fit (<1e-3). *(B)* Profile of the goodness to fit over the grid of scanned morphology parameters. Shown with two randomly picked examples in different range of goodness to fit.
[[./figs/fitting.png]]
